---
title: "Predicting the brexit vote"
author: ""
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

- In this exercise, we will work on a classification task of Brexit referendum vote
- The data is originally from British Election Study Online Panel
  - codebook: https://www.britishelectionstudy.com/wp-content/uploads/2020/05/Bes_wave19Documentation_V2.pdf
- The outcome is `LeaveVote` (1: Leave, 0: Remain)

## Libraries

- We will use the following packages

```{r}
library(tidyverse)
library(caret)
library(glmnet)
```

## Load data

We sub-sample the data. Full data takes too much time to estimate for the class... (Feel free to run full sample after the class)

```{r}
set.seed(20200813)
df_brexit <- read_csv("data/data_bes.csv.gz") %>%
  sample_n(3000) # sampling data so
```


## Data preparation

- We will carry out:
  - make `LeaveVote` factor variable
  - test train split
  - preprocess


```{r}
df_brexit <- df_brexit %>%
    mutate(LeaveVote = factor(LeaveVote))
```

### Train-test split

```{r}
set.seed(42)
train_idx <- createDataPartition(df_brexit$LeaveVote, p = .7, list = F) %>%
  as.vector()

df_train <- df_brexit %>% slice(train_idx)
df_test <- df_brexit %>% slice(-train_idx)
```

### Preprocess

```{r}
prep <- preProcess(df_train %>% select(-LeaveVote), method = c("center", "scale"))
prep

df_train_preped <- predict(prep, df_train)
df_test_preped <- predict(prep, df_test)

```

## Model formulas

There are four logistic regression models  in the manuscript (Table 2).

1. Sociodemographics
2. Identity
3. Anti-elite
4. Attitudes

The following line of codes will generate the each model. 

```{r}
fm_socdem <- formula("LeaveVote ~ gender + age + edlevel + hhincome + econPersonalRetro1")
fm_identity <- formula("LeaveVote ~ gender + age + edlevel + hhincome + 
                        EuropeanIdentity + EnglishIdentity + BritishIdentity")
fm_antielite <- formula("LeaveVote ~ gender + age + edlevel + hhincome + 
              PolMistrust + GovDisapproval + PopulismScale + 
              ConVote + LabVote + LibVote + SNPPCVote + UKIP")
fm_attitudes <- formula("LeaveVote ~ gender + age + edlevel + hhincome + euUKNotRich + 
              euNotPreventWar + FreeTradeBad + euParlOverRide1 + euUndermineIdentity1 + 
              lessEUmigrants + effectsEUTrade1 + effectsEUImmigrationLower")
fm_all <- formula("LeaveVote ~ .")


```

You can use these formulas in a way like:

```{r eval = F}
# for model
glm(fm_socdem, data = df_train_preped, family = "binomial")
# for data extraction
model.matrix(fm_socdem, data = df_train_preped) %>% head()

```

## Logistic regression

Run a few models, and evaluate them. Which one has the better predictive performance?

```{r}
mod_log_socdem <- glm(fm_socdem, data = df_train_preped, family = "binomial")
pred_log_socdem_train <- mod_log_socdem %>% predict(newdata = df_train_preped, 
                                                    type = 'response') #%>%
pred_log_socdem_train <- as.numeric(pred_log_socdem_train > .5) %>% factor()

pred_log_socdem_train <- mod_log_socdem %>% predict(newdata = df_train_preped, 
                                                    type = 'response') %>%
  `>`(.5) %>% as.numeric() %>% factor()

confusionMatrix(pred_log_socdem_train, df_train_preped$LeaveVote, 
                positive = '1', mode = "prec_recall")

pred_log_socdem_test <- mod_log_socdem %>% predict(newdata = df_test_preped, 
                                                    type = 'response') #%>%
pred_log_socdem_test <- as.numeric(pred_log_socdem_test > .5) %>% factor()

pred_log_socdem_test <- mod_log_socdem %>% predict(newdata = df_test_preped, 
                                                    type = 'response') %>%
  `>`(.5) %>% as.numeric() %>% factor()

confusionMatrix(pred_log_socdem_test, df_test_preped$LeaveVote, 
                positive = '1', mode = "prec_recall")

```
```{r}

print_conf <- function(fm, print_train = F) {
  mod_log <- glm(fm, data = df_train_preped, family = "binomial")
  pred_log_train <- mod_log %>% predict(newdata = df_train_preped, 
                                                      type = 'response') %>%
    `>`(.5) %>% as.numeric() %>% factor()
  if(print_train == T) {
    print(confusionMatrix(pred_log_train, df_train_preped$LeaveVote, 
                  positive = '1', mode = "prec_recall"))
  }
  pred_log_test <- mod_log %>% predict(newdata = df_test_preped, 
                                                      type = 'response') %>%
    `>`(.5) %>% as.numeric() %>% factor()
  
  print(confusionMatrix(pred_log_test, df_test_preped$LeaveVote, 
                  positive = '1', mode = "prec_recall"))
}


print_conf(fm_identity)
```
```{r}
conf_m <- confusionMatrix(pred_log_socdem_test, df_test_preped$LeaveVote, 
                positive = '1', mode = "prec_recall")
conf_m$byClass['F1']

```


## Linear SVM

- Train a linear SVM model, check the predictive performance. How does it compare to the logistic regression?

```{r}
mod_lsvm_socdem <- train(fm_socdem, 
                        data = df_train_preped, 
                        method = 'svmLinear')
mod_lsvm_socdem
pred_lsvm_socdem_train <- mod_lsvm_socdem %>% predict(newdata = df_train_preped)
confusionMatrix(pred_lsvm_socdem_train, df_train_preped$LeaveVote, 
                positive = '1', mode = "prec_recall")
pred_lsvm_socdem_test <- mod_lsvm_socdem %>% predict(newdata = df_test_preped)
confusionMatrix(pred_lsvm_socdem_test, df_test_preped$LeaveVote, 
                positive = '1', mode = "prec_recall")


```


```{r}

print_train_result <- 
  function(fm, method = "svmLinear", 
           print_train = F,
           tuneGrid = NULL, # NEW
           print_model = F
           ) {
  ctrl <- trainControl(method = 'repeatedcv')
  mod_temp <- train(fm, 
                    data = df_train_preped, 
                    trControl = ctrl,
                    tuneGrid = tuneGrid, 
                    method = method)
  if(print_model) print(mod_temp)
  pred_train <- mod_temp %>% predict(newdata = df_train_preped)
  if(print_train) {
    print(confusionMatrix(pred_train, df_train_preped$LeaveVote, 
                  positive = '1', mode = "prec_recall"))
  }
  pred_test <- mod_temp %>% predict(newdata = df_test_preped)
  
  print(confusionMatrix(pred_test, df_test_preped$LeaveVote, 
                positive = '1', mode = "prec_recall"))
}

print_train_result(fm_all)
```


## Polynomial SVM and Radial SVM

- Train non-linear SVM. How is the performance? Any improvement?

```{r cache=T}
print_train_result(fm_all, method = "svmRadial", 
                   print_model = T)

## customized tunegrid
print_train_result(fm_all, method = "knn", 
                   tuneGrid = data.frame(k = c(2:10, 20, 40, 50)),
                   print_model = T)


```


## (Optional) Logistic regression with LASSO

- `glmnet` can run a Logistic model with L1 penalty (LASSO). 
- Try a "full" model combining all inputs.
  - Which inputs survived?

```{r}
mat_train_x <- df_train_preped %>% select(-LeaveVote) %>% as.matrix()
mat_test_x <- df_test_preped %>% select(-LeaveVote) %>% as.matrix()

```


```{r}
mod_lasso <- cv.glmnet(mat_train_x, 
                       df_train_preped$LeaveVote, 
          alpha = 1, 
          family = "binomial")

coef(mod_lasso)
plot(mod_lasso)
plot(mod_lasso$glmnet.fit, xvar = "lambda")

pred_train <- as.integer(predict(mod_lasso, newx = mat_train_x) > 0) %>% factor()
pred_test <- as.integer(predict(mod_lasso, newx = mat_test_x) > 0) %>% factor()

confusionMatrix(df_test_preped$LeaveVote, pred_test, 
                      positive = '1', 
                      mode = "everything")

```

- The model eliminates all varirables other than identidy and issues. 

```{r}

plotmo::plot_glmnet(mod_lasso$glmnet.fit, xvar = "lambda")

```


### Model comparison with map

#### Running a lot of logistic regressions and printout cofusion matrix

```{r, eval = F}
list_fm <- list(fm_all, fm_socdem, fm_identity, fm_antielite, fm_attitudes)
list_fm %>% map(print_conf)
```

#### use the contents of confusion matrix for model comparision

##### Define new function

- This function create a single row dataframe from a confusion matrix after a model estimation

```{r}

get_conf <- function(fm = fm_all) {
  mod_log <- glm(fm, data = df_train_preped, family = "binomial")
  pred_log_test <- mod_log %>% predict(newdata = df_test_preped, 
                                                      type = 'response') %>%
    `>`(.5) %>% as.numeric() %>% factor()
  conf <- confusionMatrix(pred_log_test, df_test_preped$LeaveVote, 
                  positive = '1', mode = "prec_recall")
  c(conf$overall, conf$byClass) %>% as.list() %>% as_tibble()
}

get_conf(fm_socdem)
```
#### using the function, we can generate a data.frame of model performance

```{r}

df_fm <- tibble(modname = c("All", "SocDem", "Identity", "AntiElite", "Attitudes"), 
                  fm = c(fm_all, fm_socdem, fm_identity, fm_antielite, fm_attitudes)) 
df_fm <- df_fm %>%
  mutate(conf = map(fm, get_conf)) # get a confusion matrix output using the new function

df_fm # the dataframe is "nested" 

## unnest
df_fm %>%
  unnest(conf) 
  
```


