---
title: "Predicting the brexit vote: Tree-based method"
author: ""
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

- In this assignment, we will work on a classification task of brexit referendum vote
- The data is originally from British Election Study Online Panel
- The outcome is `LeaveVote` (1: Leave, 0: Remain)

## Libraries

- We will use the following packages

```{r}
library(tidyverse)
library(caret)
library(tree)
```

## Load data

We sub-sample the data. Full data takes too much time to estimate for the class... (Feel free to run full sample after the class)

```{r}
set.seed(20200813)
data_brexit <- read_csv("data/data_bes.csv.gz") %>%
  sample_n(3000) # sampling data so
```


## Data preparation

- We will carry out:
  - make `LeaveVote` factor variable
  - test train split
  - preprocess


```{r}
data_brexit <- data_brexit %>%
    mutate(LeaveVote = factor(LeaveVote))
```

### Train-test split

```{r}
train_idx <- createDataPartition(data_brexit$LeaveVote, p = .7, list = F) 

data_train <- data_brexit %>% slice(train_idx)
data_test <- data_brexit %>% slice(-train_idx)
```

### Preprocess

```{r}
prep <- preProcess(data_train %>% select(-LeaveVote), method = c("center", "scale"))
prep

data_train_preped <- predict(prep, data_train)
data_test_preped <- predict(prep, data_test)

```

## Model formulas

There are four logistic regression models  in the manuscript (Table 2).

1. Sociodemographics
2. Identity
3. Anti-elite
4. Attitudes

The following line of codes will generate the each model. 

```{r}
fm_socdem <- formula("LeaveVote ~ gender + age + edlevel + hhincome + econPersonalRetro1")
fm_identity <- formula("LeaveVote ~ gender + age + edlevel + hhincome + 
                        EuropeanIdentity + EnglishIdentity + BritishIdentity")
fm_antielite <- formula("LeaveVote ~ gender + age + edlevel + hhincome + 
              PolMistrust + GovDisapproval + PopulismScale + 
              ConVote + LabVote + LibVote + SNPPCVote + UKIP")
fm_attitudes <- formula("LeaveVote ~ gender + age + edlevel + hhincome + euUKNotRich + 
              euNotPreventWar + FreeTradeBad + euParlOverRide1 + euUndermineIdentity1 + 
              lessEUmigrants + effectsEUTrade1 + effectsEUImmigrationLower")
fm_all <- formula("LeaveVote ~ .")

```


## Simple tree method

- Estimate a simple classification tree, using one of the formula above. 
- Draw tree
- Evaluate the model
- What do you find?

```{r}

mod_tree <- tree(fm_all, data=df_train)
plot(mod_tree)
text(mod_tree)
pred_test_tree <- predict(mod_tree, newdata = df_test, type = 'class') 
confusionMatrix(pred_test_tree, df_test_preped$LeaveVote, positive = "1", 
                mode = "prec_recall")
```

## Random forest regression and adaBoost

- Now, run "forest" models
- Any improvement of the prediction?
- For random forest training, use `tuneGrid = data.frame(mtry = c(2:4))`. Otherwise it's too slow...

```{r cache=T}
ctrl <- trainControl(method = 'repeatedcv')
mod_rf <- train(fm_attitudes,
                data = df_train_preped, 
                method = "rf", 
                trControl = ctrl, 
                tuneGrid = data.frame(mtry = c(2:4)))
mod_rf

pred_test_rf <- predict(mod_rf, newdata = df_test_preped)
confusionMatrix(pred_test_rf, df_test_preped$LeaveVote, positive = "1", 
                mode = "prec_recall")


mod_ada <- train(fm_attitudes,
                  data = df_train_preped, 
                  trControl = ctrl, 
                  method = "ada")
mod_ada

pred_test_ada <- predict(mod_ada, newdata = data_test_preped)
confusionMatrix(pred_test_ada, data_test_preped$LeaveVote, positive = "1", 
                mode = "prec_recall")

```
