---
title: "Process a lot of files with map()"
author: ""
date: ""
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

In this exercise you will work with a lot of data files. The data come from EuroParl dataset (https://www.statmt.org/europarl/). I extracted english speeches and kept speaker's name, speech contents, and date, and then split the data to each month and saved. 

#### get the data

```{r}
dir.create("tmp")
if(!file.exists("tmp/europarl-data.zip")){
  download.file("https://www.dropbox.com/s/kr6hg7z5wj9ohu8/europarl-data.zip?dl=1", 
                destfile = "tmp/europarl-data.zip")
  unzip("tmp/europarl-data.zip", exdir = "tmp")
}
```

### Load packages

```{r}
library(tidyverse)
library(data.table)
library(DBI)
library(microbenchmark)

```

### First step: check a sample 

1. Get the list of files 
2. Open the first file

```{r}
files <- list.files('tmp/europarl-data/', pattern = 'tar', full.names = T)
length(files)
(tmp <- files[1] %>% vroom::vroom())
```

### How `map()` works

- Similar to `lapply()`
  - `lapply` returns a list of the same length as `X`, each element of which is the result of applying `FUN` to the corresponding element of `X`.
- `map()` is a tidyverse version of it. You can use an anonymous function `~`

```{r}
vec <- 1:10
lapply(vec, function(x) 1 + x)
map(vec, function(x) 1 + x)
map(vec, ~ `+`(1, .x))
```

### Open all files and combine

Once you get a list of files you can easily combine files in a single data.frame. Options would be

1. `lapply` + `fread`
2. `map` + `vroom::vroom` (or `read_csv`)

```{r}
microbenchmark(
df_1 <- lapply(files, fread) %>% rbindlist(),
df_2 <- map(files, vroom::vroom, show_col_types = F) %>% bind_rows() ,
times = 1)
```

### put files into a table in a sqlite database

```{r}
library(DBI)
file.remove("tmp_db.sqlite")
db <- dbConnect(RSQLite::SQLite(), "tmp_db.sqlite")

files %>% 
  map(~vroom::vroom(.x, show_col_types=F) %>% 
  dbWriteTable(db, "speech", ., append = T))

dbDisconnect(db)

### or you can use for-loop
file.remove("tmp_db.sqlite")

db <- dbConnect(RSQLite::SQLite(), "tmp_db.sqlite")

for (fn in files){
  df_temp <- vroom::vroom(fn, show_col_types=F)
  dbWriteTable(db, "speech", df_temp, append = T)
}

dbDisconnect(db)

```


#### Benchmarking: combine all files and write to a table or sequentially put each file in a table?

```{r}
library(DBI)
microbenchmark(
  combine_write = 
    {df <- map_dfr(files, vroom::vroom, show_col_types = F);
     df %>% dbWriteTable(db, "speech", .)},
  seq_write = 
    {files %>% map(
      ~ vroom::vroom(.x, show_col_types=F) %>% 
        dbWriteTable(db, "speech", ., append = T)) ;},
  times = 1,
  setup = {file.remove("tmp_db.sqlite"); 
    db <- dbConnect(RSQLite::SQLite(), "tmp_db.sqlite")}
)
```



