---
title: "Process a lot of files with parallelization"
author: ""
date: "20/08/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

In this exercise you will work with a lot of data files. The data come from EuroParl dataset (https://www.statmt.org/europarl/). I extracted english speeches and kept speaker's name, speech contents, and date, and then split the data to each month and saved. 

#### get the data

```{r}
dir.create("tmp")
if(!file.exists("tmp/europarl-data.zip")){
  download.file("https://www.dropbox.com/s/kr6hg7z5wj9ohu8/europarl-data.zip?dl=1", 
                destfile = "tmp/europarl-data.zip")
  unzip("tmp/europarl-data.zip", exdir = "tmp")
}
```

### Load packages

```{r}
library(tidyverse)
library(stringi)
library(data.table)
library(parallel)
library(furrr)
library(microbenchmark)
library(SentimentAnalysis)

```

### First step: check a sample 

1. Get the list of files 
2. Open the first file

```{r}
files <- list.files('tmp/europarl-data/', pattern = 'tar', full.names = T)
length(files)
(tmp <- files[1] %>% fread())
```

### Open all files and combine

There are several ways to open all files and combine
1. `lapply` + `fread`
2. `map_dfr` + `read_csv` (pure tidyverse solution)
3. `map_dfr` + `fread` 

```{r}
df_1 <- lapply(files, fread) %>% rbindlist()
df_2 <- map_dfr(files, read_csv) 
df_3 <- map_dfr(files, ~fread(.x)) 
```
### Open all files and combine, multi-thread

```{r}
detectCores()
microbenchmark::microbenchmark(
df_1 <- mclapply(files, fread, mc.cores = 4) %>% rbindlist(),
{plan(multisession, workers = 4); df_4 <- future_map(files, ~fread(.x)) %>% rbindlist()},
times = 1)
```


### SentimentAnalysis package

- One of the popular options for dictionary based sentiment analyais in R is `SentimentAnalsyis` package.
- It work like this:

```{r}
analyzeSentiment(tmp$text[1:10]) 
```

## Incorporate the sentiment analysis as a part of processing

- Attach results column from SentimentGI to PositivityQDAP (13 columns)

### `mcapply`

```{r}
tictoc::tic()
files %>% 
  head() %>%
  mclapply(function(x){
  c_data <- fread(x) 
  vad <- analyzeSentiment(c_data$text) %>% select(SentimentGI:PositivityQDAP) 
  return(bind_cols(c_data, vad))
}, mc.cores = detectCores() * .7 )
tictoc::toc()
```
### `map_dfr`

```{r}
tictoc::tic()
plan(multisession, workers = detectCores() * .7)---
title: "Process a lot of files with parallelization"
author: ""
date: "20/08/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

In this exercise you will work with a lot of data files. The data come from EuroParl dataset (https://www.statmt.org/europarl/). I extracted english speeches and kept speaker's name, speech contents, and date, and then split the data to each month and saved. 

#### get the data

```{r}
dir.create("tmp")
if(!file.exists("tmp/europarl-data.zip")){
  download.file("https://www.dropbox.com/s/kr6hg7z5wj9ohu8/europarl-data.zip?dl=1", 
                destfile = "tmp/europarl-data.zip")
  unzip("tmp/europarl-data.zip", exdir = "tmp")
}
```

### Load packages

```{r}
library(tidyverse)
library(stringi)
library(data.table)
library(parallel)
library(furrr)
library(microbenchmark)
library(SentimentAnalysis)

```

### First step: check a sample 

1. Get the list of files 
2. Open the first file

```{r}
files <- list.files('tmp/europarl-data/', pattern = 'tar', full.names = T)
length(files)
(tmp <- files[1] %>% fread())
```

### Open all files and combine

There are several ways to open all files and combine
1. `lapply` + `fread`
2. `map_dfr` + `read_csv` (pure tidyverse solution)
3. `map_dfr` + `fread` 

```{r}
df_1 <- lapply(files, fread) %>% rbindlist()
df_2 <- map_dfr(files, read_csv) 
df_3 <- map_dfr(files, ~fread(.x)) 
```
### Open all files and combine, multi-thread

```{r}
detectCores()
```

```{r}
microbenchmark::microbenchmark(
df_1 <- mclapply(files, fread, mc.cores = 4) %>% rbindlist(),
{plan(multisession, workers = 4); df_4 <- future_map(files, ~fread(.x)) %>% rbindlist()},
times = 1)
```


### SentimentAnalysis package

- One of the popular options for dictionary based sentiment analyais in R is `SentimentAnalsyis` package.
- It work like this:

```{r}
analyzeSentiment(tmp$text[1:10]) 
```

## Incorporate the sentiment analysis as a part of processing

- Attach results column from SentimentGI to PositivityQDAP (13 columns)

### `mcapply`

```{r}
tictoc::tic()
df_out <- files %>% 
  head() %>%
  mclapply(function(x) {
  c_data <- fread(x) 
  vad <- analyzeSentiment(c_data$text) %>% select(SentimentGI:PositivityQDAP) %>% setDT
  return(cbind(c_data, vad))
}, mc.cores = detectCores() * .7 )
tictoc::toc()
```
### `map_dfr`

```{r}
tictoc::tic()
plan(multisession, workers = detectCores() * .7)
df_out <- files %>% 
  head() %>%
  future_map(function(x){
  c_data <- fread(x) 
  vad <- analyzeSentiment(c_data$text) %>% select(SentimentGI:PositivityQDAP) %>% setDT
  return(cbind(c_data, vad))
}) %>% bind_rows()
tictoc::toc()
```


---
title: "Process a lot of files with parallelization"
author: ""
date: "20/08/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

In this exercise you will work with a lot of data files. The data come from EuroParl dataset (https://www.statmt.org/europarl/). I extracted english speeches and kept speaker's name, speech contents, and date, and then split the data to each month and saved. 

#### get the data

```{r}
dir.create("tmp")
if(!file.exists("tmp/europarl-data.zip")){
  download.file("https://www.dropbox.com/s/kr6hg7z5wj9ohu8/europarl-data.zip?dl=1", 
                destfile = "tmp/europarl-data.zip")
  unzip("tmp/europarl-data.zip", exdir = "tmp")
}
```

### Load packages

```{r}
library(tidyverse)
library(stringi)
library(data.table)
library(parallel)
library(furrr)
library(microbenchmark)
library(SentimentAnalysis)

```

### First step: check a sample 

1. Get the list of files 
2. Open the first file

```{r}
files <- list.files('tmp/europarl-data/', pattern = 'tar', full.names = T)
length(files)
(tmp <- files[1] %>% fread())
```

### Open all files and combine

There are several ways to open all files and combine
1. `lapply` + `fread`
2. `map_dfr` + `read_csv` (pure tidyverse solution)
3. `map_dfr` + `fread` 

```{r}
df_1 <- lapply(files, fread) %>% rbindlist()
df_2 <- map_dfr(files, read_csv) 
df_3 <- map_dfr(files, ~fread(.x)) 
```
### Open all files and combine, multi-thread

```{r}
detectCores()
```

```{r}
microbenchmark::microbenchmark(
df_1 <- mclapply(files, fread, mc.cores = 4) %>% rbindlist(),
{plan(multisession, workers = 4); df_4 <- future_map(files, ~fread(.x)) %>% rbindlist()},
times = 1)
```


### SentimentAnalysis package

- One of the popular options for dictionary based sentiment analyais in R is `SentimentAnalsyis` package.
- It work like this:

```{r}
analyzeSentiment(tmp$text[1:10]) 
```

## Incorporate the sentiment analysis as a part of processing

- Attach results column from SentimentGI to PositivityQDAP (13 columns)

### `mcapply`

```{r}
tictoc::tic()
df_out <- files %>% 
  head() %>%
  mclapply(function(x) {
  c_data <- fread(x) 
  vad <- analyzeSentiment(c_data$text) %>% select(SentimentGI:PositivityQDAP) %>% setDT
  return(cbind(c_data, vad))
}, mc.cores = detectCores() * .7 )
tictoc::toc()
```
### `map_dfr`

```{r}
tictoc::tic()
plan(multisession, workers = detectCores() * .7)
df_out <- files %>% 
  head() %>%
  future_map(function(x){
  c_data <- fread(x) 
  vad <- analyzeSentiment(c_data$text) %>% select(SentimentGI:PositivityQDAP) %>% setDT
  return(cbind(c_data, vad))
}) %>% bind_rows()
tictoc::toc()
```



df_out <- files %>% 
  head() %>%
  future_map(function(x){
  c_data <- fread(x) 
  vad <- analyzeSentiment(c_data$text) %>% select(SentimentGI:PositivityQDAP) 
  return(bind_cols(c_data, vad))
}) %>% bind_rows()
tictoc::toc()
```


